SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-05-03 papers/B1555_EdgeOn/B1555_letter.tex
Add about K+03 flux ratio measurements

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image
positions and flux densities measured by the radio observations of
\citet{Marlow99}, \textbf{who also} presented a singular isothermal ellipsoid
(SIE) model that provided the first fit[a good fit--John/ but It's not good compare to our model--JW] to the image positions but
does not reproduce the strong flux-ratio anomaly between components A
and B.  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
Although the flux-ratio anomaly that is observed in the radio data \textbf{implies there must be some perturbation to the mass model, which} may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the \textit{HST} infrared imaging (\textbf{see} in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux-ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the \textbf{non-}detection of these
images.

@@

\textbf{For each model, we explore the parameter space in the following way: 
(1) Preparation of priors: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \deg$ to the edge-on disk component. We then use the best-fit model of \citet{Marlow99} as the starting point for the bulge\textbf{/halo} component and also the source position. The rest of parameters in the disk component are set to be the same as the bulge/halo component as the starting point.
(2) Markov Chain Monte Carlo: In {\tt glafic}, we run MCMC to find the a proper set of parameters for further optimization. The smallest $\chi^2$ doesn't necessarily give a physical model. Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimize [CHECK THE ALGORITHM?] to reach the final best-fit for each model.}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4117 $  &   $+0.0280$ \\  
D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1619$    &  $+0.3680$ \\  
\hline
\end{tabular}

@@

In this letter, we focus on the effect of more complicated mass
distributions for the lens galaxy on flux-ratio anomalies.
Traditionally, flux anomalous lensed quasars are radio-loud systems
that are firstly discovered in radio observations. While radio data
provide reliable information on the positions and the fluxes of the
lensed images, they are often unable to detect the lens
galaxies. Moreover, lens modelling based only on the positions of the
four images can be highly degenerate and prior assumptions play a key
role in the interpretation of the observed flux-ratio anomaly.  Since
lens galaxies are typically at redshifts of $z \leq 1$, optical and
near-infrared observations are ideal for measuring the light distribution
of lens galaxies and obtaining useful prior information on the underlying
mass distributions. Indeed \citet{SHARP12} showed that high
resolution IR imaging can help to significantly improve the precision
of the lens modelling. This improvement is even more dramatic in the
case of B1555+375, where \textit{HST} and SHARP AO high resolution imaging has
allowed us to detect, for the fist time, the presence of an edge-on
disk. This newly discovered edge-on disk provides a strong prior for our
lens modelling.  With \textbf{an additional disk component}, our models produce
matches to both the radio image positions and their flux-ratio, wheras
models with only one SIE component \citep{Marlow99,Xu14} fail to
reproduce the fluxes correctly. Our successful modelling indicates
that the kiloparsec-scale structure of the lens galaxy itself is
sufficient to explain the flux-ratio anomalies in B1555+375, without
any need to invoke the presence of substructure.

>>>>

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image
positions and flux densities measured by the radio observations.
\textbf{We use the image positions from \citet{Marlow99}, who also presented a singular isothermal ellipsoid
(SIE) model that provided a good fit to the image positions but
does not reproduce the strong flux-ratio anomaly between components A
and B.}  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
\textbf{The flux measurements are performed by \citet{K03} with a half year monitoring to obtain flux-ratio curves, providing throughout discussions in erros on flux densities than in \citet{Marlow}.}

Although the flux-ratio anomaly that is observed in the radio data \textbf{implies there must be some perturbation to the mass model, which} may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the \textit{HST} infrared imaging (\textbf{see} in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux-ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the \textbf{non-}detection of these
images.

@@

\textbf{For each model, we explore the parameter space in the following way: 
(1) Preparation of priors: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the edge-on disk component. We then use the best-fit model of \citet{Marlow99} as the starting point for the bulge\textbf{/halo} component and also the source position. The rest of parameters in the disk component are set to be the same as the bulge/halo component as the starting point.
(2) Markov Chain Monte Carlo: In {\tt glafic}, we run MCMC to find the a proper set of parameters for further optimization. The smallest $\chi^2$ doesn't necessarily give a physical model. Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4117 $  &   $-0.0280$ \\  
D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1619$    &  $-0.3680$ \\  
\hline
\end{tabular}

@@

In this letter, we \textbf{instead} focus on the effect that more complicated lens galaxy mass
distributions \textbf{have} on flux-ratio anomalies.
Traditionally, flux-anomalous lensed quasars \textbf{have been} radio-loud, initially discovered in radio observations. While radio data
provide reliable information on the positions and the fluxes of the
lensed images, they are often unable to detect the lens
galaxies. Moreover, lens modelling based only on the positions of the
four images can be highly degenerate and prior assumptions play a key
role in the interpretation of the observed flux-ratio anomaly.  Since
lens galaxies are typically at redshifts of $z \leq 1$, optical and
near-infrared observations are ideal for measuring the light distribution
of lens galaxies and obtaining useful prior information on the underlying
mass distributions. Indeed \citet{SHARP12} showed that high
resolution IR imaging can help to significantly improve the precision
of the lens modelling. This improvement is even more dramatic in the
case of B1555+375, where \textit{HST} and SHARP AO high resolution imaging has
allowed us to detect, for the fist time, the presence of an edge-on
disk. This newly discovered edge-on disk provides a strong prior for our
lens modelling.  With \textbf{an additional disk component}, our models produce
matches to both the radio image positions and their flux-ratio, wheras
models with only one SIE component \citep{Marlow99,Xu14} fail to
reproduce the fluxes correctly. Our successful modelling indicates
that the kiloparsec-scale structure of the lens galaxy itself is
sufficient to explain the flux-ratio anomalies in B1555+375, without
any need to invoke the presence of substructure.
